---
title: "Cell-cell interactions with CellChat"
output:
  html_document:
    df_print: paged
  pdf_document: default
---
## Cell-cell interactions for in vitro samples (7 hours post vaccination)

```{r setup, include=FALSE}
#knitr::opts_chunk$set(dev = 'pdf')
```


```{r load_libraries, echo = F}
# libraries
#devtools::install_github("sqjin/CellChat")
#devtools::install_github("thomasp85/patchwork")

suppressPackageStartupMessages(library(CellChat))
suppressPackageStartupMessages(library(patchwork))
suppressPackageStartupMessages(library(ComplexHeatmap))
suppressPackageStartupMessages(library(circlize))
suppressPackageStartupMessages(library(RColorBrewer))
suppressPackageStartupMessages(library(svglite))
suppressPackageStartupMessages(library(NMF))
suppressPackageStartupMessages(library(ggalluvial))
#library(pheatmap)
options(stringsAsFactors = FALSE)
#options(bitmapType="cairo")
```

```{r clusters, echo = F}
levels(cellchat@idents)
```

### Condition 1: Control


```{r show_cond1, echo = F}
# Pick a condition
# BNT162b2 or AZD1222 or Ctrl
cellchat <- readRDS("~/Documents/charite/Sophia/cellchat_7h_Ctrl.rds")

cellchat <- computeCommunProbPathway(cellchat)
cellchat@netP$pathways
```


```{r CCC_signaling1, echo = F}

#Infer the cell-cell communication at a signaling pathway level

#CellChat computes the communication probability on signaling pathway level by summarizing the communication probabilities of all ligands-receptors interactions associated with each signaling pathway.

#NB: The inferred intercellular communication network of each ligand-receptor pair and each signaling pathway is stored in the slot ‘net’ and ‘netP’, respectively.
cellchat <- aggregateNet(cellchat)
pathways.show <- c("CCL") 

groupSize <- as.numeric(table(cellchat@idents))
par(mfrow = c(1,2), xpd=TRUE)
netVisual_circle(cellchat@net$count, vertex.weight = groupSize, weight.scale = T, label.edge= F, title.name = "Number of interactions")
netVisual_circle(cellchat@net$weight, vertex.weight = groupSize, weight.scale = T, label.edge= F, title.name = "Interaction weights/strength")

mat <- cellchat@net$weight
par(mfrow = c(3,4), xpd=TRUE)
for (i in 1:nrow(mat)) {
  mat2 <- matrix(0, nrow = nrow(mat), ncol = ncol(mat), dimnames = dimnames(mat))
  mat2[i, ] <- mat[i, ]
  netVisual_circle(mat2, vertex.weight = groupSize, weight.scale = T, edge.weight.max = max(mat), title.name = rownames(mat)[i])
}

# Hierarchy plot
# Here we define `vertex.receive` so that the left portion of the hierarchy plot shows signaling to fibroblast and the right portion shows signaling to immune cells 
vertex.receiver = seq(1,4) # a numeric vector. 
netVisual_aggregate(cellchat, signaling = pathways.show,  vertex.receiver = vertex.receiver, layout = "hierarchy")
```

```{r ch1, echo = F}
# Chord diagram
par(mfrow=c(1,1))
netVisual_aggregate(cellchat, signaling = pathways.show, layout = "chord")

```

```{r cont1, echo = F}
par(mfrow=c(1,1))
netVisual_heatmap(cellchat, signaling = pathways.show, color.heatmap = "Reds")
cellchat.C <- cellchat
pairLR.CCL <- extractEnrichedLR(cellchat, signaling = pathways.show, geneLR.return = FALSE)
LR.show <- pairLR.CCL[1,]

netAnalysis_contribution(cellchat, signaling = pathways.show)

netVisual_individual(cellchat, signaling = pathways.show,  pairLR.use = LR.show, vertex.receiver = vertex.receiver, layout = "hierarchy")
```

```{r, echo = F}

netVisual_individual(cellchat, signaling = pathways.show, pairLR.use = LR.show, layout = "circle")

```

```{r multiple_LR1, echo = F}
# show all the significant interactions (L-R pairs) from some cell groups (defined by 'sources.use') to other cell groups (defined by 'targets.use')
netVisual_bubble(cellchat, sources.use = c(9), targets.use = c(2,5,6), remove.isolate = FALSE)
#> Comparing communications on a single object

# show all the significant interactions (L-R pairs) associated with certain signaling pathways
netVisual_bubble(cellchat, sources.use = c(9), targets.use = c(2, 5, 6, 8), signaling = pathways.show, remove.isolate = FALSE)
#> Comparing communications on a single object
```

```{r chord1, echo = F}
# show all the significant interactions (L-R pairs) from some cell groups (defined by 'sources.use') to other cell groups (defined by 'targets.use')
# show all the interactions sending from Inflam.FIB
netVisual_chord_gene(cellchat, sources.use = c(9), targets.use =c(2,5,6), lab.cex = 0.5,legend.pos.y = 30)

# show all the interactions received by Inflam.DC
netVisual_chord_gene(cellchat, sources.use = c(9), targets.use = c(2,5,6), legend.pos.x = 15)

# show all the significant interactions (L-R pairs) associated with certain signaling pathways
netVisual_chord_gene(cellchat, sources.use = c(9), targets.use = c(2,5,6), signaling = c("CCL", "CXCL"),legend.pos.x = 8)
#> Note: The second link end is drawn out of sector 'CXCR4 '.
#> Note: The first link end is drawn out of sector 'CXCL12 '.
```


### Plot the signaling gene expression distribution using violin/dot plot

```{r violins1, echo = F}
plotGeneExpression(cellchat, signaling = pathways.show,  enriched.only = T)
#> Registered S3 method overwritten by 'spatstat':
#>   method     from
#>   print.boxx cli
#> Scale for 'y' is already present. Adding another scale for 'y', which will
#> replace the existing scale.
#> Scale for 'y' is already present. Adding another scale for 'y', which will
#> replace the existing scale.
#> Scale for 'y' is already present. Adding another scale for 'y', which will
#> replace the existing scale.

```

### Part IV: Systems analysis of cell-cell communication network

```{r sys1, echo = F}
# Compute the network centrality scores
cellchat <- netAnalysis_computeCentrality(cellchat, slot.name = "netP") # the slot 'netP' means the inferred intercellular communication network of signaling pathways
# Visualize the computed centrality scores using heatmap, allowing ready identification of major signaling roles of cell groups
netAnalysis_signalingRole_network(cellchat, signaling = pathways.show, width = 8, height = 2.5, font.size = 10)
```

```{r dom1, echo = F}
#Visualize the dominant senders (sources) and receivers (targets) in a 2D space

#We also provide another intutive way to visualize the dominant senders (sources) and receivers (targets) in a 2D space using scatter plot.

# Signaling role analysis on the aggregated cell-cell communication network from all signaling pathways
gg1 <- netAnalysis_signalingRole_scatter(cellchat)
#> Signaling role analysis on the aggregated cell-cell communication network from all signaling pathways
# Signaling role analysis on the cell-cell communication networks of interest
gg2 <- netAnalysis_signalingRole_scatter(cellchat, signaling = c("CXCL", "CCL"))
#> Signaling role analysis on the cell-cell communication network from user's input
gg1 + gg2
```

```{r cont_1, echo = F}
# Signaling role analysis on the aggregated cell-cell communication network from all signaling pathways
ht1 <- netAnalysis_signalingRole_heatmap(cellchat, pattern = "outgoing")
ht2 <- netAnalysis_signalingRole_heatmap(cellchat, pattern = "incoming")
ht1 + ht2

# Signaling role analysis on the cell-cell communication networks of interest
ht <- netAnalysis_signalingRole_heatmap(cellchat, signaling = c("CXCL", "CCL"))
ht
```

```{r patterns1, echo = F}
CellChat::selectK(cellchat, pattern = "outgoing")
nPatterns = 3
cellchat <- identifyCommunicationPatterns(cellchat, pattern = "outgoing", k = nPatterns)

# river plot
netAnalysis_river(cellchat, pattern = "outgoing")
#> Please make sure you have load `library(ggalluvial)` when running this function

# dot plot
netAnalysis_dot(cellchat, pattern = "outgoing")

cellchat.C <- cellchat
```

### Condition 2: AZD


```{r show_cond2, echo = F}
# Pick a condition
# BNT162b2 or AZD1222 or Ctrl
cellchat <- readRDS("~/Documents/charite/Sophia/cellchat_7h_AZD.rds")

cellchat <- computeCommunProbPathway(cellchat)
cellchat@netP$pathways
```


```{r CCC_signaling2, echo = F}

#Infer the cell-cell communication at a signaling pathway level

#CellChat computes the communication probability on signaling pathway level by summarizing the communication probabilities of all ligands-receptors interactions associated with each signaling pathway.

#NB: The inferred intercellular communication network of each ligand-receptor pair and each signaling pathway is stored in the slot ‘net’ and ‘netP’, respectively.
cellchat <- aggregateNet(cellchat)

pathways.show <- c("CCL") 
pathways.show <- cellchat@netP$pathways

groupSize <- as.numeric(table(cellchat@idents))
par(mfrow = c(1,2), xpd=TRUE)
netVisual_circle(cellchat@net$count, vertex.weight = groupSize, weight.scale = T, label.edge= F, title.name = "Number of interactions")
netVisual_circle(cellchat@net$weight, vertex.weight = groupSize, weight.scale = T, label.edge= F, title.name = "Interaction weights/strength")

mat <- cellchat@net$weight
par(mfrow = c(3,4), xpd=TRUE)
for (i in 1:nrow(mat)) {
  mat2 <- matrix(0, nrow = nrow(mat), ncol = ncol(mat), dimnames = dimnames(mat))
  mat2[i, ] <- mat[i, ]
  netVisual_circle(mat2, vertex.weight = groupSize, weight.scale = T, edge.weight.max = max(mat), title.name = rownames(mat)[i])
}

# Hierarchy plot
# Here we define `vertex.receive` so that the left portion of the hierarchy plot shows signaling to fibroblast and the right portion shows signaling to immune cells 
vertex.receiver = seq(1,4) # a numeric vector. 
netVisual_aggregate(cellchat, signaling = pathways.show,  vertex.receiver = vertex.receiver, layout = "hierarchy")
```

```{r ch2, echo = F}
# Chord diagram
par(mfrow=c((length(pathways.show)/3), 3))
netVisual_aggregate(cellchat, signaling = pathways.show, layout = "chord")

```

```{r cont2, echo = F}
par(mfrow=c(1,1))
netVisual_heatmap(cellchat, signaling = pathways.show, color.heatmap = "Reds")
cellchat.A <- cellchat
pairLR.CCL <- extractEnrichedLR(cellchat, signaling = pathways.show, geneLR.return = TRUE)

LR.show <- pairLR.CCL[1,]

netAnalysis_contribution(cellchat, signaling = pathways.show, font.size = 4, return.data = T)


netVisual_individual(cellchat, signaling = pathways.show,  pairLR.use = LR.show, vertex.receiver = vertex.receiver, layout = "circle")
```

```{r, echo = F}

netVisual_individual(cellchat, signaling = pathways.show, pairLR.use = LR.show, layout = "circle")

```

```{r multiple_LR2, echo = F}
# show all the significant interactions (L-R pairs) from some cell groups (defined by 'sources.use') to other cell groups (defined by 'targets.use')
netVisual_bubble(cellchat, sources.use = c(9), targets.use = c(2,5,6), remove.isolate = FALSE)
#> Comparing communications on a single object

# show all the significant interactions (L-R pairs) associated with certain signaling pathways
netVisual_bubble(cellchat, sources.use = c(9), targets.use = c(2, 5, 6, 8), signaling = pathways.show, remove.isolate = FALSE)
#> Comparing communications on a single object
```

```{r chord2, echo = F}
# show all the significant interactions (L-R pairs) from some cell groups (defined by 'sources.use') to other cell groups (defined by 'targets.use')
# show all the interactions sending from Inflam.FIB
#netVisual_chord_gene(cellchat, sources.use = c(9), targets.use =c(5,6), lab.cex = 0.5,legend.pos.y = 30)

# show all the interactions received by Inflam.DC
#netVisual_chord_gene(cellchat, sources.use = c(9), targets.use = c(2,5,6), legend.pos.x = 15)

# show all the significant interactions (L-R pairs) associated with certain signaling pathways
netVisual_chord_gene(cellchat, sources.use = c(9), targets.use = c(2,5,6), signaling = c("CCL", "CXCL"),legend.pos.x = 8)
#> Note: The second link end is drawn out of sector 'CXCR4 '.
#> Note: The first link end is drawn out of sector 'CXCL12 '.
```

### Plot the signaling gene expression distribution using violin/dot plot

```{r violins2, echo = F}
plotGeneExpression(cellchat, signaling = "CCL",  enriched.only = T)
#> Registered S3 method overwritten by 'spatstat':
#>   method     from
#>   print.boxx cli
#> Scale for 'y' is already present. Adding another scale for 'y', which will
#> replace the existing scale.
#> Scale for 'y' is already present. Adding another scale for 'y', which will
#> replace the existing scale.
#> Scale for 'y' is already present. Adding another scale for 'y', which will
#> replace the existing scale.

```

### Part IV: Systems analysis of cell-cell communication network

```{r sys2, echo = F}
# Compute the network centrality scores
cellchat <- netAnalysis_computeCentrality(cellchat, slot.name = "netP") # the slot 'netP' means the inferred intercellular communication network of signaling pathways
# Visualize the computed centrality scores using heatmap, allowing ready identification of major signaling roles of cell groups
netAnalysis_signalingRole_network(cellchat, signaling = pathways.show, width = 8, height = 2.5, font.size = 10)
```

```{r dom2, echo = F}
#Visualize the dominant senders (sources) and receivers (targets) in a 2D space

#We also provide another intutive way to visualize the dominant senders (sources) and receivers (targets) in a 2D space using scatter plot.

# Signaling role analysis on the aggregated cell-cell communication network from all signaling pathways
gg1 <- netAnalysis_signalingRole_scatter(cellchat)
#> Signaling role analysis on the aggregated cell-cell communication network from all signaling pathways
# Signaling role analysis on the cell-cell communication networks of interest
gg2 <- netAnalysis_signalingRole_scatter(cellchat, signaling = c("CXCL", "CCL"))
#> Signaling role analysis on the cell-cell communication network from user's input
gg1 + gg2
```

```{r cont_2, echo = F}
# Signaling role analysis on the aggregated cell-cell communication network from all signaling pathways
ht1 <- netAnalysis_signalingRole_heatmap(cellchat, pattern = "outgoing")
ht2 <- netAnalysis_signalingRole_heatmap(cellchat, pattern = "incoming")
ht1 + ht2

# Signaling role analysis on the cell-cell communication networks of interest
ht <- netAnalysis_signalingRole_heatmap(cellchat, signaling = c("CXCL", "CCL"))
ht
```

```{r patterns2, echo = F}
selectK(cellchat, pattern = "outgoing")
nPatterns = 3
cellchat <- identifyCommunicationPatterns(cellchat, pattern = "outgoing", k = nPatterns)

# river plot
netAnalysis_river(cellchat, pattern = "outgoing")
#> Please make sure you have load `library(ggalluvial)` when running this function

# dot plot
netAnalysis_dot(cellchat, pattern = "outgoing")
```


```{r CCC_signaling2.5, scho = F}

#Infer the cell-cell communication at a signaling pathway level

#CellChat computes the communication probability on signaling pathway level by summarizing the communication probabilities of all ligands-receptors interactions associated with each signaling pathway.

#NB: The inferred intercellular communication network of each ligand-receptor pair and each signaling pathway is stored in the slot ‘net’ and ‘netP’, respectively.

pathways.show <- c("IFN-I") 

groupSize <- as.numeric(table(cellchat@idents))
par(mfrow = c(1,2), xpd=TRUE)
netVisual_circle(cellchat@net$count, vertex.weight = groupSize, weight.scale = T, label.edge= F, title.name = "Number of interactions")
netVisual_circle(cellchat@net$weight, vertex.weight = groupSize, weight.scale = T, label.edge= F, title.name = "Interaction weights/strength")

mat <- cellchat@net$weight
par(mfrow = c(3,4), xpd=TRUE)
for (i in 1:nrow(mat)) {
  mat2 <- matrix(0, nrow = nrow(mat), ncol = ncol(mat), dimnames = dimnames(mat))
  mat2[i, ] <- mat[i, ]
  netVisual_circle(mat2, vertex.weight = groupSize, weight.scale = T, edge.weight.max = max(mat), title.name = rownames(mat)[i])
}

# Hierarchy plot
# Here we define `vertex.receive` so that the left portion of the hierarchy plot shows signaling to fibroblast and the right portion shows signaling to immune cells 
vertex.receiver = seq(1,4) # a numeric vector. 
netVisual_aggregate(cellchat, signaling = pathways.show,  vertex.receiver = vertex.receiver, layout = "hierarchy")
```

```{r ch2.5, echo = F}
# Chord diagram
par(mfrow=c(1,1))
netVisual_aggregate(cellchat, signaling = pathways.show, layout = "chord")

```

```{r cont_2.5, echo = F}
par(mfrow=c(1,1))
netVisual_heatmap(cellchat, signaling = pathways.show, color.heatmap = "Reds")

pairLR.IFN <- extractEnrichedLR(cellchat, signaling = pathways.show, geneLR.return = FALSE)
netAnalysis_contribution(cellchat, signaling = pathways.show)

LR.show <- pairLR.IFN[1,]

netVisual_individual(cellchat, signaling = pathways.show,  pairLR.use = LR.show, vertex.receiver = vertex.receiver, layout = "hierarchy")
```


```{r, echo = F}

netVisual_individual(cellchat, signaling = pathways.show, pairLR.use = LR.show, layout = "circle")

```


```{r multiple_LR2.5, echo = F}
# show all the significant interactions (L-R pairs) from some cell groups (defined by 'sources.use') to other cell groups (defined by 'targets.use')
netVisual_bubble(cellchat, sources.use = c(9), targets.use = c(2,5,6), remove.isolate = FALSE)
#> Comparing communications on a single object

# show all the significant interactions (L-R pairs) associated with certain signaling pathways
netVisual_bubble(cellchat, sources.use = c(9), targets.use = c(2, 5, 6, 8), signaling = pathways.show, remove.isolate = FALSE)
#> Comparing communications on a single object
```

```{r chord2.5, echo = F}
# show all the significant interactions (L-R pairs) from some cell groups (defined by 'sources.use') to other cell groups (defined by 'targets.use')
# show all the interactions sending from Inflam.FIB
netVisual_chord_gene(cellchat, sources.use = c(9), targets.use =c(2,5,6), lab.cex = 0.5,legend.pos.y = 30)

# show all the interactions received by Inflam.DC
netVisual_chord_gene(cellchat, sources.use = c(9), targets.use = c(2,5,6), legend.pos.x = 15)

# show all the significant interactions (L-R pairs) associated with certain signaling pathways
netVisual_chord_gene(cellchat, sources.use = c(9), targets.use = c(2,5,6), signaling = c("IFN-I"),legend.pos.x = 8)
#> Note: The second link end is drawn out of sector 'CXCR4 '.
#> Note: The first link end is drawn out of sector 'CXCL12 '.
```

### Plot the signaling gene expression distribution using violin/dot plot

```{r violins2.5, echo = F}
plotGeneExpression(cellchat, signaling = "IFN-I",  enriched.only = T)
#> Registered S3 method overwritten by 'spatstat':
#>   method     from
#>   print.boxx cli
#> Scale for 'y' is already present. Adding another scale for 'y', which will
#> replace the existing scale.
#> Scale for 'y' is already present. Adding another scale for 'y', which will
#> replace the existing scale.
#> Scale for 'y' is already present. Adding another scale for 'y', which will
#> replace the existing scale.

```

### Part IV: Systems analysis of cell-cell communication network

```{r sys2.5, echo = F}
# Compute the network centrality scores
cellchat <- netAnalysis_computeCentrality(cellchat, slot.name = "netP") # the slot 'netP' means the inferred intercellular communication network of signaling pathways
# Visualize the computed centrality scores using heatmap, allowing ready identification of major signaling roles of cell groups
netAnalysis_signalingRole_network(cellchat, signaling = pathways.show, width = 8, height = 2.5, font.size = 10)
```

```{r dom2.5, echo = F}
#Visualize the dominant senders (sources) and receivers (targets) in a 2D space

#We also provide another intutive way to visualize the dominant senders (sources) and receivers (targets) in a 2D space using scatter plot.

# Signaling role analysis on the aggregated cell-cell communication network from all signaling pathways
gg1 <- netAnalysis_signalingRole_scatter(cellchat)
#> Signaling role analysis on the aggregated cell-cell communication network from all signaling pathways
# Signaling role analysis on the cell-cell communication networks of interest
gg2 <- netAnalysis_signalingRole_scatter(cellchat, signaling = c("IFN-I"))
#> Signaling role analysis on the cell-cell communication network from user's input
gg1 + gg2
```

<!-- ```{r cont2.5, echo = F} -->
<!-- # Signaling role analysis on the aggregated cell-cell communication network from all signaling pathways -->
<!-- ht1 <- netAnalysis_signalingRole_heatmap(cellchat, pattern = "outgoing") -->
<!-- ht2 <- netAnalysis_signalingRole_heatmap(cellchat, pattern = "incoming") -->
<!-- ht1 + ht2 -->

<!-- # Signaling role analysis on the cell-cell communication networks of interest -->
<!-- ht <- netAnalysis_signalingRole_heatmap(cellchat, signaling = c("IFN-I")) -->
<!-- ht -->
<!-- ``` -->

```{r patterns2.5, echo = F}
selectK(cellchat, pattern = "outgoing")
nPatterns = 3
cellchat <- identifyCommunicationPatterns(cellchat, pattern = "outgoing", k = nPatterns)

# river plot
netAnalysis_river(cellchat, pattern = "outgoing")
#> Please make sure you have load `library(ggalluvial)` when running this function

# dot plot
netAnalysis_dot(cellchat, pattern = "outgoing")
```


### Condition 3: BNT


```{r show_cond3, echo = F}
# Pick a condition
# BNT162b2 or AZD1222 or Ctrl
cellchat <- readRDS("~/Documents/charite/Sophia/cellchat_7h_BNT.rds")

cellchat <- computeCommunProbPathway(cellchat)
cellchat@netP$pathways
```


```{r CCC_signaling3, echo = F}

#Infer the cell-cell communication at a signaling pathway level

#CellChat computes the communication probability on signaling pathway level by summarizing the communication probabilities of all ligands-receptors interactions associated with each signaling pathway.

#NB: The inferred intercellular communication network of each ligand-receptor pair and each signaling pathway is stored in the slot ‘net’ and ‘netP’, respectively.
cellchat <- aggregateNet(cellchat)

pathways.show <- c("CCL") 

groupSize <- as.numeric(table(cellchat@idents))
par(mfrow = c(1,2), xpd=TRUE)
netVisual_circle(cellchat@net$count, vertex.weight = groupSize, weight.scale = T, label.edge= F, title.name = "Number of interactions")
netVisual_circle(cellchat@net$weight, vertex.weight = groupSize, weight.scale = T, label.edge= F, title.name = "Interaction weights/strength")

mat <- cellchat@net$weight
par(mfrow = c(3,4), xpd=TRUE)
for (i in 1:nrow(mat)) {
  mat2 <- matrix(0, nrow = nrow(mat), ncol = ncol(mat), dimnames = dimnames(mat))
  mat2[i, ] <- mat[i, ]
  netVisual_circle(mat2, vertex.weight = groupSize, weight.scale = T, edge.weight.max = max(mat), title.name = rownames(mat)[i])
}

# Hierarchy plot
# Here we define `vertex.receive` so that the left portion of the hierarchy plot shows signaling to fibroblast and the right portion shows signaling to immune cells 
vertex.receiver = seq(1,4) # a numeric vector. 
netVisual_aggregate(cellchat, signaling = pathways.show,  vertex.receiver = vertex.receiver, layout = "hierarchy")
```

```{r ch5, echo = F}
# Chord diagram
par(mfrow=c(1,1))
netVisual_aggregate(cellchat, signaling = pathways.show, layout = "chord")

```

```{r cont3, echo = F}
par(mfrow=c(1,1))
netVisual_heatmap(cellchat, signaling = pathways.show, color.heatmap = "Reds")
cellchat.B <- cellchat
pairLR.CCL <- extractEnrichedLR(cellchat, signaling = pathways.show, geneLR.return = FALSE)

LR.show = pairLR.CCL[1,]

netAnalysis_contribution(cellchat, signaling = pathways.show)

netVisual_individual(cellchat, signaling = pathways.show,  pairLR.use = LR.show, vertex.receiver = vertex.receiver, layout = "hierarchy")

```


```{r, echo = F}

netVisual_individual(cellchat, signaling = pathways.show, pairLR.use = LR.show, layout = "circle")

```


```{r multiple_LR3, echo = F}
# show all the significant interactions (L-R pairs) from some cell groups (defined by 'sources.use') to other cell groups (defined by 'targets.use')
netVisual_bubble(cellchat, sources.use = c(2), targets.use = c(2,5,6), remove.isolate = FALSE)
#> Comparing communications on a single object

# show all the significant interactions (L-R pairs) associated with certain signaling pathways
netVisual_bubble(cellchat, sources.use = c(2), targets.use = c(2, 5, 6, 8), signaling = pathways.show, remove.isolate = FALSE)
#> Comparing communications on a single object
```

```{r chord3, echo = F}
# show all the significant interactions (L-R pairs) from some cell groups (defined by 'sources.use') to other cell groups (defined by 'targets.use')
# show all the interactions sending from Inflam.FIB
netVisual_chord_gene(cellchat, sources.use = c(2), targets.use =c(5,6), lab.cex = 0.5,legend.pos.y = 30)

# show all the interactions received by Inflam.DC
netVisual_chord_gene(cellchat, sources.use = c(2), targets.use = c(5,6), legend.pos.x = 15)

# show all the significant interactions (L-R pairs) associated with certain signaling pathways
netVisual_chord_gene(cellchat, sources.use = c(2), targets.use = c(5,6), signaling = c("CCL", "CXCL"),legend.pos.x = 8)
#> Note: The second link end is drawn out of sector 'CXCR4 '.
#> Note: The first link end is drawn out of sector 'CXCL12 '.
```

### Plot the signaling gene expression distribution using violin/dot plot

```{r violins3, echo = F}
plotGeneExpression(cellchat, signaling = "CCL",  enriched.only = T)
#> Registered S3 method overwritten by 'spatstat':
#>   method     from
#>   print.boxx cli
#> Scale for 'y' is already present. Adding another scale for 'y', which will
#> replace the existing scale.
#> Scale for 'y' is already present. Adding another scale for 'y', which will
#> replace the existing scale.
#> Scale for 'y' is already present. Adding another scale for 'y', which will
#> replace the existing scale.

```

### Part IV: Systems analysis of cell-cell communication network

```{r sys3, echo = F}
# Compute the network centrality scores
cellchat <- netAnalysis_computeCentrality(cellchat, slot.name = "netP") # the slot 'netP' means the inferred intercellular communication network of signaling pathways
# Visualize the computed centrality scores using heatmap, allowing ready identification of major signaling roles of cell groups
netAnalysis_signalingRole_network(cellchat, signaling = pathways.show, width = 8, height = 2.5, font.size = 10)
```

```{r dom3, echo = F}
#Visualize the dominant senders (sources) and receivers (targets) in a 2D space

#We also provide another intutive way to visualize the dominant senders (sources) and receivers (targets) in a 2D space using scatter plot.

# Signaling role analysis on the aggregated cell-cell communication network from all signaling pathways
gg1 <- netAnalysis_signalingRole_scatter(cellchat)
#> Signaling role analysis on the aggregated cell-cell communication network from all signaling pathways
# Signaling role analysis on the cell-cell communication networks of interest
gg2 <- netAnalysis_signalingRole_scatter(cellchat, signaling = c("CXCL", "CCL"))
#> Signaling role analysis on the cell-cell communication network from user's input
gg1 + gg2
```

```{r cont_3, echo = F}
# Signaling role analysis on the aggregated cell-cell communication network from all signaling pathways
ht1 <- netAnalysis_signalingRole_heatmap(cellchat, pattern = "outgoing")
ht2 <- netAnalysis_signalingRole_heatmap(cellchat, pattern = "incoming")
ht1 + ht2

# Signaling role analysis on the cell-cell communication networks of interest
ht <- netAnalysis_signalingRole_heatmap(cellchat, signaling = c("CXCL", "CCL"))
ht
```

```{r patterns3, echo = F}
selectK(cellchat, pattern = "outgoing")
nPatterns = 3
cellchat <- identifyCommunicationPatterns(cellchat, pattern = "outgoing", k = nPatterns)

# river plot
netAnalysis_river(cellchat, pattern = "outgoing")
#> Please make sure you have load `library(ggalluvial)` when running this function

# dot plot
netAnalysis_dot(cellchat, pattern = "outgoing")

```

### Common pathways in the three conditions

```{r intersections, echo = F, fig.height=18}
CTR.p <- data.frame(Pathway = cellchat.C@netP$pathways) %>%
  mutate(Ctrl = rep(1, length(cellchat.C@netP$pathways)))
  
AZD.p <- data.frame(Pathway = cellchat.A@netP$pathways) %>%
  mutate(AZD = rep(1, length(cellchat.A@netP$pathways)))

BNT.p <- data.frame(Pathway = cellchat.B@netP$pathways) %>%
  mutate(BNT = rep(1, length(cellchat.B@netP$pathways)))

heatmap.counter <- 
  plyr::join_all(list(CTR.p, AZD.p, BNT.p), by='Pathway', type='full') %>%
  mutate_all(~replace(., is.na(.), 0)) %>%
  tibble::column_to_rownames("Pathway")


#par(cex.main = 2)
#pheatmap(heatmap.counter, cluster_rows = F, cluster_cols = F, scale = "none", cellwidth = 2, cellheight = 2, legend = F, annotation_legend = F, main = "Enriched pathways at 18 hours", fontsize = 5 )

#{heatmap(as.matrix(heatmap.counter), Colv = NA, Rowv = NA,scale = "none", cexCol = 1, bty = "o", col = colorRampPalette(brewer.pal(3,"Blues"))(3), main = "Enriched pathways at 18 hours") ; legend(x="bottomright", legend=c("Absent", "Present"), fill = colorRampPalette(brewer.pal(3, "Blues"))(3), xjust = 1, cex = 0.7)}

col_fun = colorRamp2(c(0, 1), c("blue", "red"))
at = seq(0, 1, by = 1)
lgd = Legend(at = at, title = "Presence", legend_gp = gpar(fill = col_fun(at)))
hm <- Heatmap(as.matrix(heatmap.counter), width = ncol(heatmap.counter)*unit(5, "mm"), 
    height = nrow(heatmap.counter)*unit(5, "mm"),
    cluster_rows = T, show_row_dend = F, show_column_dend = F,
    show_heatmap_legend = F, row_names_gp = grid::gpar(fontsize = 7), column_names_gp = grid::gpar(fontsize = 7))

draw(hm, annotation_legend_list = lgd, annotation_legend_side = "right")
```


